Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-07 analysis/paper/paper.qmd
Table 3

>>>>

Note: the repeated cells in the first column of [@tbl-indicators] must be merged manually to produce the formatting seen in the published paper.

```{r}
#| label: tbl-indicators
#| tbl-cap: "Indicator species for each predator cluster. Indicator values are the product of relative frequency and relative abundance, ranging from 0 to 1. Only species with indicator values ≥0.25 are shown for each cluster. See Methods for details."

make_indicatortbl(read_obj("sightings_indval"))
